```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
```

\   

# Marker features {.tabset .tabset-pills .tabset-fade}
## By TMA spots {.tabset .tabset-pills .tabset-fade}
### Marker extent
```{r MTHFD1L_extent}
x <- marker$MTHFD1L_ext
g_nice(x, bin = 10)
tbl_nice(x)
```

### Marker intensity
```{r MTHFD1L_intensity}
x <- factor(marker$MTHFD1L_int)
g_nice(x)
tbl_nice(x)
```

### Marker H-score
```{r MTHFD1L_h}
x <- marker$MTHFD1L_h
g_nice(x, bin = 25)
tbl_nice(x)
```

***

## By SP cases {.tabset .tabset-pills .tabset-fade}
### By median value {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r MTHFD1L_ext_med}
x <- DF$MTHFD1L_ext_med
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r MTHFD1L_int_med}
x <- factor(DF$MTHFD1L_int_med)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r MTHFD1L_h_med}
x <- DF$MTHFD1L_h_med
g_nice(x, bin = 25)
tbl_nice(x)
```

### By maximum value {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r MTHFD1L_ext_max}
x <- DF$MTHFD1L_ext_max
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r MTHFD1L_int_max}
x <- factor(DF$MTHFD1L_int_max)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r MTHFD1L_h_max}
x <- DF$MTHFD1L_h_max
g_nice(x, bin = 25)
tbl_nice(x)
```
